A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-09 papers/publication/paper-pollard.tex
Updated abstract.

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{\{spollard,norris\}@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
There are an intimidating number of parallel graph processing systems. One survey in 2014 identified over 80. Since then, the landscape has changed; some packages have become inactive, even more have been introduced, and previous top performers have been usurped. To address the high churn of projects and the complexity of selecting a system for a given problem, we analyze the performance and scalability of four parallel open source graph processing systems (GraphMat, GAP Benchmark Suite, GraphBIG, and PowerGraph) using synthetic and real-world datasets. We perform analysis for three algorithms: breadth first search, single source shortest paths, and PageRank. We then compare our results to the most comprehensive parallel graph processing performance and benchmarking project: Graphalytics. We examine previously overlooked aspects of parallel graph processing performance such as energy usage in addition to a performance analysis model based on the Graph500.
\end{abstract}

>>>>

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{\{spollard,norris\}@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
The increasing popularity of large network analysis problems has led to the emergence of many parallel and distributed graph processing systems---one survey in 2014 identified over 80. Since then, the landscape has evolved; some packages have become inactive while more are being developed. Determining the best approach for a given problem is infeasible for most developers. To enable easy, rigorous, and repeatable comparison of the capabilities of such systems, we present an approach and associated software for analyzing the performance and scalability of parallel, open-source graph processing systems. We demonstrate our approach on five graph frameworks: GraphMat, the Graph500, the Graph Algorithm Platform, GraphBIG, and PowerGraph using synthetic and real-world datasets. We examine previously overlooked aspects of parallel graph processing performance such as phases of execution and energy usage for three algorithms: breadth first search, single source shortest paths, and PageRank and compare our results to Graphalytics.
\end{abstract}
